---
title: "Cabbages"
author: "Syslee Evans "
date: "May 31, 2022"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  
$H_O$: There is no difference between the vitC content based on the cultivation method c39 and c52.

$H_A$: There is a difference between the vitC based on the cultivation method c39 and c52.  


# Methods
we are explaining a vitamine c numerical variable by by explaining the catagorical variable cultivation. We will use the T-test to comare the mean of the two vitamine C from the 
<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results


### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
boxplot(VitC~Cult,data=veggy)
```

The catagory C39 looks like it has an overall lower mean for the numerical result of vitamine C. While the C52 catagory had a higher mean of the vitamine C using their cultivation method.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
favstats(VitC~Cult,data=veggy)
```
The cultivation method C39 had a median of 51.0 while C52 had a median of 64.5. C39 had a mean of 51.5 and C52 had a mean of 64.4 meaning that the cultivation method c52 was more successful in producing a high average of vitamine C.

## Inferential Results
```{r}
t.test(VitC~Cult,data=veggy)
```

Based in our two sample T test we can infer the the p-value is 0.00000003405  from this we can reject the null hypothisis because the probability of the sample result was very unlikley, meaning that the null hypothisis is falese. 
<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
